---
title: "HW1_BY"
author: "Billy Yuan"
date: "2/3/2017"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/Dropbox/MSBA/Spring 2016/Stochastic Control/Group Proj/Group Proj 1")
library(lpSolve)
```

### Question 1

Assume that bond purchases are made at the beginning of time 1

Let $p$ be the vector of bond prices 
$$p = \begin{bmatrix} 102 & 99 & 101 & 98 & 98 & 104 & 100 & 101 & 102 & 94 \end{bmatrix}$$

Let $c$ be the vector of bond coupon payments 

$$c = \begin{bmatrix} 5 & 3.5 & 5 & 3.5 & 4 & 9 & 6 & 8 & 9 & 7 \end{bmatrix}$$

$u$ is the vector containing maturity for the N bonds
$$u = \begin{bmatrix} 100 &... &100 \end{bmatrix}$$

$\mathbf{M}$ is the matrix of size $t \times n$ where $t$ is the number of years and $n$ is the bond number and where $M_{t,n}$ is whether bond $n$ has reached maturity at time $t$. Below: the 1st, 2nd, 3rd and 8th rows are shown, while columns 1-4 and 8-10 are shown.

$$ \mathbf{M} = \begin{bmatrix} 1 & 0 & 0 & 0 & ... & 0 & 0 & 0 \\ 0 & 1 & 1 & 0 & ... & 0 &  0 & 0 \\0 & 0 & 0 & 1 & ... & 0 &  0 & 0 \\... \\ 0 & 0 & 0 & 0 & ... & 0 & 0 & 1 \end{bmatrix}$$


$\mathbf{B}$ is the  $t \times n$ matrix indicating whether there's a coupon payment in year $t$ for bond $n$

$$ \mathbf{B} = \begin{bmatrix} 1 & 1 & 1 & 1 & ... & 1 & 1 & 1 \\ 0 & 1 & 1 & 1 & ... & 0 &  0 & 0 \\ 0 & 0 & 0 & 1 & ... & 0 &  0 & 0 \\... \\ 0 & 0 & 0 & 0 & ... & 0 & 0 & 1 \end{bmatrix}$$

Thus, the following can be expressed:

* $\sum_{i=1}^{n}b_{t,i}c_{i}$ is the cash inflow from coupon payments from bonds $1$ to $n$ at time $t$
* $\sum_{i=1}^{n}m_{t,i}u_{i}$ is the cash inflow from maturity from bonds $1$ to $n$ at time $t$
* $\sum_{i=1}^{n}z^{i}$ is the total excess funds from time 1 to $n$

**Decision Variables**

* $x_{1}$ to $x_{10}$ are the number of bonds of each type from 1 to 10 that are purchased


**Objective**

* Minimize $\sum_{i=1}^{10}p_{i}x_{i}$ where $p_{i}$ is the price of bond $i$

**Constraints**

* $\sum_{i=1}^{10}(b_{i,t}c_{i} + m_{i,t}u_{i}) \times x_{i} \geq l_{t}$ where $t$ is year

* $x_{i} \geq 0$


### Question 2

```{r}
p <- c(102, 99, 101, 98, 98, 104, 100, 101, 102, 94) # prices of bonds 1-10
c <- c(5, 3.5, 5, 3.5, 4, 9, 6, 8, 9, 7) # coupon payments of bonds 1-10
u <- rep(100, 10) # maturity payment of bonds 1-10
m <- c(1,2,2,3,4,5,5,6,7,8) # years to maturity for bonds 1-10


# x1 to x10 are columns 1-10
c.model <- p

# Equality constraints
b <- c(12000, 18000, 20000, 20000, 16000, 15000, 12000, 10000) # liabilities
b <- append(b, rep(0,10)) # non-negative

# Direction
dir <- c(rep(">=",8),rep(">=",10))

# Helper matrices

M <- matrix(0, nrow = 8, ncol = 10) # M matrix for whether maturity payment is made
B <- matrix(0, nrow=8, ncol = 10) # B matrix is for whether coupon payment is made

# Fill in B & M matrix
for (bond_num in c(1:10)) {
  maturity.yr <- m[bond_num]
  coupon.yrs <- c(1:maturity.yr)
  
  M[maturity.yr, bond_num] <- 1
  B[coupon.yrs, bond_num] <- 1
}

# Create A matrix
A <- matrix(0, nrow = 18, ncol = 10)

# Fill in A matrix columns for liability constraints. Row is year and column is bond #
for (year in c(1:8)) {
  # Compute coupon and maturity payment per unit of bond
  coupon.pmt <- c * B[year,]
  maturity.pmt <- u * M[year,]
  
  # Add cash in-flow per unit of bond
  A[year,1:10] <- coupon.pmt + maturity.pmt
}


# Non-negativity 
A[9:18, 1:10] <- diag(1,10,10)

# Solve
q1 <- lp("min",c.model, A, dir, b)
q1$solution
```
